### 2018-03-13 README.Rmd
first build

---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# salinity

The goal of salinity is to ...

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

### 2018-03-13 R/peat19_processing.R

@@ -1,0 +1,99 @@
+#' Script to load, merge, and process daily to annual budgets.
+#' Code varies for each site as input met variables vary across sites
+#' Site: Peat 19 yr old
+#'
+#' @import dplyr
+#' @importFrom lubridate month
+#' @importFrom dplyr "%>%"
+
+# load eddy flux and met dataset
+load("data/peat19_all.Rdata")
+peat19_all$dday <- floor(peat19_all$decday)
+peat19_all$site <- "Mature"
+
+#Simple average of daily fluxes for gapfilled values
+daily <- peat19_all %>%
+  group_by(dday, site) %>%
+  summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            vNEE = mean(wc_gf_var),     #NEE variance (umol m-2 s-1)^2
+            c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
+            mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
+            m_obs = sum(!is.na(wm)),
+            GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
+            ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
+            ET = mean(wq_gf),           #evapotranspiration (mmol m-2 s-1)
+            q_obs = sum(!is.na(wq)),
+            H = mean(H_gf),             #sensible heat flux (W m-2)
+            mGCC = mean(GCC, na.rm=T),  #green index
+            PAR = mean(PAR, na.rm=T),   #photosynthetic active radiation (umol m-2 s-1)
+            Tair = mean(TA.y, na.rm=T), #air temp (deg C)
+            Tw = mean(TW_8cm, na.rm=T), #water temp (deg C)
+            Ts = mean(TS_8cm, na.rm=T), #soil temp (deg C)
+            mVPD = mean(VPD, na.rm=T),  #VPD (kPa)
[…]

### 2018-03-13 R/peat6_processing.R

@@ -1,0 +1,99 @@
+#' Script to load, merge, and process daily to annual budgets.
+#' Code varies for each site as input met variables vary across sites
+#' Site: Peat 6 yr old
+#'
+#' @import dplyr
+#' @importFrom lubridate month
+#' @importFrom dplyr "%>%"
+
+# load eddy flux and met dataset
+load("data/peat6_all.Rdata")
+peat6_all$dday <- floor(peat6_all$decday)
+
+#Simple average of daily fluxes for gapfilled values
+daily <- peat6_all %>%
+  group_by(dday, site) %>%
+  summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            vNEE = mean(wc_gf_var),     #NEE variance (umol m-2 s-1)^2
+            c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
+            mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
+            m_obs = sum(!is.na(wm)),
+            GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
+            ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
+            ET = mean(wq_gf),           #evapotranspiration (mmol m-2 s-1)
+            q_obs = sum(!is.na(wq)),
+            H = mean(H_gf),                    #sensible heat flux (W m-2)
+            mGCC = mean(GCC, na.rm=T),   #green index
+            PAR = mean(PAR, na.rm=T),          #photosynthetic active radiation (umol m-2 s-1)
+            Tair = mean(TA.y, na.rm=T),        #air temp (deg C)
+            Tw = mean(TW_WATER_10cm, na.rm=T), #water temp (deg C)
+            Ts = mean(TS_TULE_8cm, na.rm=T),   #soil temp (deg C)
+            mVPD = mean(VPD, na.rm=T),         #VPD (kPa)
[…]

### 2018-03-13 R/salinity-package.r

@@ -1,0 +1,5 @@
+#' salinity.
+#'
+#' @name salinity
+#' @docType package
+NULL

### 2018-03-13 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(salinity)
+
+test_check("salinity")

### 2018-03-15 R/peat6_processing.R
early analysis

@@ -37,9 +37,19 @@ daily <- peat6_all %>%
             Rain = sum(PRECIP, na.rm=T),       #rain (mm)
             WTD = mean(WT, na.rm=T),           #water table (m from surface)
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
+            DOrange1 = max(DO_mid, na.rm=T) - min(DO_mid, na.rm=T),
+            DOmid = mean(DO_mid, na.rm=T),
+            DOrange2 = max(DO_deep, na.rm=T) - min(DO_deep, na.rm=T),
+            DOdiff = mean(DO_mid, na.rm=T) - mean(DO_deep, na.rm=T),
+            COrangeS = max(wCO2_open_surface_ppm, na.rm=T) - min(wCO2_open_surface_ppm, na.rm=T),
+            COrangeM = max(wCO2_open_mid_ppm, na.rm=T) - min(wCO2_open_mid_ppm, na.rm=T),
+            COrangeD = max(wCO2_open_deep_ppm, na.rm=T) - min(wCO2_open_deep_ppm, na.rm=T),
+            COdiff = mean(wCO2_open_surface_ppm, na.rm=T) - mean(wCO2_open_deep_ppm, na.rm=T),
             t_obs = length(wc_gf),      # total observations in the day
             year = round(median(year))) %>%
   filter(year > 2010 & t_obs == 48) #cut pre-wetland measures, and incomplete days at ends of time series
+
+daily[daily == -Inf] <- NaN
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2010-01-01")

### 2018-03-22 R/peat6_processing.R
big step forward on MI across time

@@ -69,6 +69,7 @@ monthly <- daily %>%
             mGEP = mean(gGEP),
             mCond = mean(Cond, na.rm=T),
             #mSal = mean(Sal, na.rm=T),
+            datetime = mean(datetime),
             days = sum(!is.na(mgCH4))) %>%
   filter(days > 27) # only complete months
 

### 2018-03-23 R/MI_functions.R
building info theory functions

@@ -1,0 +1,92 @@
+#' Script for entropy and mutual information calculations
+#' Including functions for basic MI calculations, lagged MI, and MI across time
+#'
+#' @import entropy
+#' @importFrom dplyr lag
+
+#calculate relative mutual information between two variables and designate number of bins to use
+mutual_info <- function(x, y, bins = 10) {
+
+  clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables
+
+  y2d <- discretize2d(clip_set$x, clip_set$y, numBins1 = bins, numBins2 = bins) #joint probability distribution with num of bins
+
+  y_entropy <- entropy(discretize(na.omit(y), numBins = bins)) #entropy of dependent variable
+  mi.empirical(y2d)/y_entropy #relative mutual information (standardized by entropy of y)
+}
+
+#calculate MI at multiple lags of x variable
+lag_mi <- function(x, y, lags, bins = 10, plotting = F) {
+
+  lag_mi <- vector("double", lags) #store lagged MI values
+
+  for (i in 1:lags) {
+    x_lag <- dplyr::lag(x, n = i)
+    lag_mi[[i]] <- mutual_info(x_lag, y, bins)
+  }
+
+  lag_mi
+}
+
+#calculate MI time series based on data in list form grouped by time index
+mi_timeseries <- function(x, y, data_list, bins = 10) {
+
+  mi_series <- vector("double", nrow(data_list)) #vector to store mutual information
+
+  #iterate through indexed datasets and calculate relative MI
+  for (i in 1:nrow(data_list)) {
+    current_df <- data_list$data[[i]] #extract current dataframe
+    x_var <- eval(substitute(x), current_df)
+    y_var <- eval(substitute(y), current_df)
+
+    mi_series[[i]] <- mutual_info(x_var, y_var, bins)
+  }
+  mi_series
+}
+
+#calculate correlation time series based on data in list form grouped by time index
+corr_timeseries <- function(x, y, data_list, method = "pearson") {
+
+  corr_series <- vector("double", nrow(data_list)) #vector to store correlation coefficients
+
+  #iterate through indexed datasets and calculate relative MI
+  for (i in 1:nrow(data_list)) {
+    current_df <- data_list$data[[i]] #extract current dataframe
+    x_var <- eval(substitute(x), current_df)
[…]

### 2018-03-23 R/peat6_processing.R

@@ -70,8 +70,11 @@ monthly <- daily %>%
             mCond = mean(Cond, na.rm=T),
             #mSal = mean(Sal, na.rm=T),
             datetime = mean(datetime),
-            days = sum(!is.na(mgCH4))) %>%
-  filter(days > 27) # only complete months
+            days = sum(!is.na(mgCH4)),
+            CH4_obs = sum(m_obs),
+            total_obs = sum(t_obs)) %>%
+  filter(days > 27)  %>% # only complete months
+  mutate(frac_CH4obs = CH4_obs/total_obs)
 
 # convert to monthly sums
 monthly$gCH4 <- monthly$mCH4*monthly$days/1000 #g C m-2 mnth-1

### 2018-03-27 R/MI_functions.R
Updates of main analysis

@@ -62,7 +62,7 @@ corr_timeseries <- function(x, y, data_list, method = "pearson") {
 }
 
 #calculate upper confidence bound for statistical significance
-mi_confidence <- function(x, y, runs = 1000, cutoff = 0.975) {
+mi_confidence <- function(x, y, runs = 1000) {
 
   mc_out <- rep(NA, runs) #vector for statistic output
 
@@ -71,7 +71,7 @@ mi_confidence <- function(x, y, runs = 1000, cutoff = 0.975) {
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
     mc_out[i] <- mutual_info(rand_x, y) #calculate MI between shuffled x and y
   }
-  quantile(mc_out, c(cutoff))[[1]]
+  mean(mc_out)
 }
 
 conf_series <- function(x, y, data_list, runs = 1000) {

### 2018-03-27 R/peat19_processing.R

@@ -40,7 +40,7 @@ daily <- peat19_all %>%
             Cond = mean(conductivity, na.rm=T), #conductivity (mS)
             t_obs = length(wc_gf),      # total observations in the day
             year = round(median(year))) %>%
-  filter(t_obs == 48 & year > 2013)  #remove incomplete days at either end of time series and year with water table drop issues
+  filter(t_obs == 48 & year > 2012)  #remove incomplete days at either end of time series and year with water table drop issues
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2012-01-01")
@@ -60,8 +60,12 @@ monthly <- daily %>%
             mGEP = mean(gGEP),
             mCond = mean(Cond, na.rm=T),
             #mSal = mean(Sal, na.rm=T),
-            days = sum(!is.na(mgCH4))) %>%
-  filter(days > 27) # only complete months
+            datetime = mean(datetime),
+            days = sum(!is.na(mgCH4)),
+            CH4_obs = sum(m_obs),
+            total_obs = sum(t_obs)) %>%
+  filter(days > 27)  %>% # only complete months
+  mutate(frac_CH4obs = CH4_obs/total_obs)
 
 # convert to monthly sums
 monthly$gCH4 <- monthly$mCH4*monthly$days/1000 #g C m-2 mnth-1

### 2018-04-01 R/MI_functions.R
Lots of new info theory functions

@@ -1,35 +1,45 @@
-#' Script for entropy and mutual information calculations
+#' Script for mutual information calculations
 #' Including functions for basic MI calculations, lagged MI, and MI across time
 #'
 #' @import entropy
 #' @importFrom dplyr lag
 
 #calculate relative mutual information between two variables and designate number of bins to use
-mutual_info <- function(x, y, bins = 10) {
+mutual_info <- function(x, y, bins = 10, normalize = TRUE) {
 
   clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables
 
-  y2d <- discretize2d(clip_set$x, clip_set$y, numBins1 = bins, numBins2 = bins) #joint probability distribution with num of bins
-
-  y_entropy <- entropy(discretize(na.omit(y), numBins = bins)) #entropy of dependent variable
-  mi.empirical(y2d)/y_entropy #relative mutual information (standardized by entropy of y)
+  y2d <- discretize2d(clip_set$x, clip_set$y, numBins1 = bins, numBins2 = bins) #joint distribution
+  
+  Hx <- entropy.empirical(rowSums(y2d)) #entropy x variable
+  Hy <- entropy.empirical(colSums(y2d)) #entropy y variable
+  Hxy <- entropy.empirical(y2d) #joint entropy
+  
+  if (normalize == T) {
+    I <- (Hx + Hy - Hxy)/Hy #relative mutual information
+  } else {
+    I <- (Hx + Hy - Hxy) #absolute mutual information
+  }
+  
+  return(I)
 }
 
+
 #calculate MI at multiple lags of x variable
-lag_mi <- function(x, y, lags, bins = 10, plotting = F) {
+lag_mi <- function(x, y, lags, bins = 10, normalize = TRUE) {
 
   lag_mi <- vector("double", lags) #store lagged MI values
 
-  for (i in 1:lags) {
-    x_lag <- dplyr::lag(x, n = i)
-    lag_mi[[i]] <- mutual_info(x_lag, y, bins)
+  for (i in 1:(lags+1)) {
+    x_lag <- dplyr::lag(x, n = i-1) # include syncronhous interactions
+    lag_mi[[i]] <- mutual_info(x_lag, y, bins, normalize = normalize)
   }
 
   lag_mi
 }
 
 #calculate MI time series based on data in list form grouped by time index
-mi_timeseries <- function(x, y, data_list, bins = 10) {
[…]

### 2018-04-01 R/TR_functions.R

@@ -1,0 +1,57 @@
+#' Transfer entropy (Tr) functions (following Knuth et al. 2005)
+#' Includes basic Tr calculations, lagged Tr, and Tr across time
+#'
+#' @import entropy
+#' @importFrom dplyr lag
+
+transfer_entropy <- function(x, y, xlag, ylag, bins = 10, normalize = TRUE) {
+  
+  x_lag <- dplyr::lag(x, n = xlag)
+  y_lag <- dplyr::lag(y, n = ylag)
+  
+  #clip_set <- data.frame(x_lag, y_lag, y)
+  #clip_set[!complete.cases(clip_set), ] <- NA #this follows Laurel and Ben's code
+  clip_set <- na.omit(data.frame(x_lag, y_lag, y)) #clip rows were any value is missing
+  
+  Hxy <- entropy.empirical(discretize2d(clip_set$x_lag, clip_set$y_lag, numBins1 = bins, numBins2 = bins), unit = "log2")
+  Hyy <- entropy.empirical(discretize2d(clip_set$y, clip_set$y_lag,  numBins1 = bins, numBins2 = bins), unit = "log2")
+  Hyl <- entropy.empirical(discretize(na.omit(clip_set$y_lag), numBins = bins), unit = "log2")
+  Hxyz <- entropy.empirical(discretize3d(clip_set$x_lag, clip_set$y_lag, clip_set$y, numBins = bins), unit = "log2")
+  Hy <- entropy.empirical(discretize(na.omit(clip_set$y), numBins = bins), unit = "log2") # entropy at current state
+  
+  if (normalize == T) {
+    Tr = (Hxy + Hyy - Hyl - Hxyz)/Hy
+  } else {
+    Tr = Hxy + Hyy - Hyl - Hxyz
+  }
+  return(Tr)
+}
+
+#calculate Tr at multiple lags of x variable
+lag_tr <- function(x, y, lags, bins = 10, normalize = TRUE) {
+  
+  lag_tr <- vector("double", lags) #store lagged MI values
+  
+  for (i in 1:(lags)) {
+    lag_tr[[i]] <- transfer_entropy(x, y, x_lag = i, ylag = 1, bins, normalize = normalize) # using immediate history of y
+  }
+  
+  lag_tr
+}
+
+#calculate Tr time series based on data in list form grouped by time index
+tr_timeseries <- function(x, y, data_list, bins = 10, normalize = TRUE) {
+  
[…]

### 2018-04-01 R/new_functions.R

@@ -1,0 +1,40 @@
+joint_entropy <- function(x, y, bins = 11) {
+  
+  clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables
+  r1 = range(clip_set$x); r2 = range(clip_set$y)
+  
+  # bin label for every observation of x and y
+  x_breaks <- seq(from=r1[1], to=r1[2], length.out=bins+1)
+  y_breaks <- seq(from=r2[1], to=r2[2], length.out=bins+1)
+  
+  #create vector of bin assignments
+  x_bin <- table(cut(clip_set$x, x_breaks, include.lowest = T, labels = 1:bins))
+  y_bin <- table(cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins))
+  
+  #calculate joint and marginal entropies
+  p_x <- x_bin/sum(x_bin)
+  p_y <- y_bin/sum(y_bin)
+  
+  -sum(p_y[p_y > 0]*log(p_y[p_y > 0]))
+  double <- table(cut(clip_set$x, x_breaks, include.lowest = T, labels = 1:bins), 
+                  cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins),
+                  cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins))
+  
+  double
+  #p_double <- double/sum(double)
+  #-sum(p_double[p_double > 0]*log(p_double[p_double > 0]))
+  
+}
+
+discretize3d = function( x1, x2, x3, numBins, r1=range(x1), r2=range(x2), r3=range(x3))
+  {
+  b1 = seq(from = r1[1], to = r1[2], length.out = numBins+1)
+  b2 = seq(from = r2[1], to = r2[2], length.out = numBins+1)
+  b3 = seq(from = r3[1], to = r3[2], length.out = numBins+1)
+  
+  y3d = table( cut(x1, breaks=b1, include.lowest=TRUE ), 
+               cut(x2, breaks=b2, include.lowest=TRUE ),
+               cut(x3, breaks=b3, include.lowest=TRUE ))
+  
+  return( y3d )
+}

### 2018-04-01 R/signficance_tests.R

@@ -1,0 +1,51 @@
+#' Functions for statistical signficance of mutual information and transfer entropy via
+#' Monte Carlo reshuffling of datasets. Includes functions for single test and time series
+
+#calculate confidence bound for Mutual Information statistical significance
+mi_confidence <- function(x, y, runs = 1000) {
+  
+  mc_out <- rep(NA, runs) #vector for statistic output
+  
+  for (i in 1:runs) {
+    
+    rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
+    mc_out[i] <- mutual_info(rand_x, y, normalize = T) #calculate MI between shuffled x and y
+  }
+  mean(mc_out)
+}
+
+#calculate confidence bound for Transfer Entropy statistical significance
+tr_confidence <- function(x, y, runs = 1000) {
+  
+  mc_out <- rep(NA, runs) #vector for statistic output
+  
+  for (i in 1:runs) {
+    
+    rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
+    mc_out[i] <- transfer_entropy(rand_x, y, normalize = T) #calculate MI between shuffled x and y
+  }
+  mean(mc_out)
+}
+
+#calculate times series of Monte Carlo limits
+conf_series <- function(x, y, data_list, runs = 1000, type=c("I", "T")) {
+  
+  MC_series <- vector("double", nrow(data_list))
+  
+  for (i in 1:nrow(data_list)) {
+    current_df <- data_list$data[[i]]
+    x_var <- eval(substitute(x), current_df)
+    y_var <- eval(substitute(y), current_df)
+    
+    if (type == "I") {
+      MC_mean <- mi_confidence(x_var, y_var, runs)
+    } else if (type == "T") {
+      MC_mean <- tr_confidence(x_var, y_var, runs)
+    } else {
+      return("Warning: not a valid test")
+    }
+    
+    MC_series[[i]] <- MC_mean
+  }
+  MC_series
+}

### 2018-04-02 R/TR_functions.R
4/2 work

@@ -4,7 +4,7 @@
 #' @import entropy
 #' @importFrom dplyr lag
 
-transfer_entropy <- function(x, y, xlag, ylag, bins = 10, normalize = TRUE) {
+transfer_entropy <- function(x, y, xlag, ylag = 1, bins = 10, normalize = TRUE) {
   
   x_lag <- dplyr::lag(x, n = xlag)
   y_lag <- dplyr::lag(y, n = ylag)
@@ -27,31 +27,55 @@ transfer_entropy <- function(x, y, xlag, ylag, bins = 10, normalize = TRUE) {
   return(Tr)
 }
 
+#three-way joint distributions for transfer entropy calculation
+discretize3d = function( x1, x2, x3, numBins, r1=range(x1), r2=range(x2), r3=range(x3))
+{
+  b1 = seq(from = r1[1], to = r1[2], length.out = numBins+1)
+  b2 = seq(from = r2[1], to = r2[2], length.out = numBins+1)
+  b3 = seq(from = r3[1], to = r3[2], length.out = numBins+1)
+  
+  y3d = table( cut(x1, breaks=b1, include.lowest=TRUE ), 
+               cut(x2, breaks=b2, include.lowest=TRUE ),
+               cut(x3, breaks=b3, include.lowest=TRUE ))
+  
+  return( y3d )
+}
+
 #calculate Tr at multiple lags of x variable
 lag_tr <- function(x, y, lags, bins = 10, normalize = TRUE) {
   
   lag_tr <- vector("double", lags) #store lagged MI values
   
   for (i in 1:(lags)) {
-    lag_tr[[i]] <- transfer_entropy(x, y, x_lag = i, ylag = 1, bins, normalize = normalize) # using immediate history of y
+    lag_tr[[i]] <- transfer_entropy(x, y, xlag = i, ylag = 1, bins, normalize = normalize) # using immediate history of y
   }
   
   lag_tr
 }
 
 #calculate Tr time series based on data in list form grouped by time index
-tr_timeseries <- function(x, y, data_list, bins = 10, normalize = TRUE) {
+tr_timeseries <- function(x, y, data_list, lags, bins = 10, normalize = TRUE, type = c("observed", "shuffled")) {
   
-  tr_series <- vector("double", nrow(data_list)) #vector to store transfer entropy
+  output_list <- list()
+  #tr_series <- data.frame("double", ncol(data_list), nrow(lags)) #vector to store transfer entropy
   
   #iterate through indexed datasets and calculate Tr
[…]

### 2018-04-02 R/signficance_tests.R

@@ -2,33 +2,33 @@
 #' Monte Carlo reshuffling of datasets. Includes functions for single test and time series
 
 #calculate confidence bound for Mutual Information statistical significance
-mi_confidence <- function(x, y, runs = 1000) {
+mi_confidence <- function(x, y, runs = 1000, bins = 10, normalize = T) {
   
   mc_out <- rep(NA, runs) #vector for statistic output
   
   for (i in 1:runs) {
     
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
-    mc_out[i] <- mutual_info(rand_x, y, normalize = T) #calculate MI between shuffled x and y
+    mc_out[i] <- mutual_info(rand_x, y, bins = bins, normalize = normalize) #calculate MI between shuffled x and y
   }
   mean(mc_out)
 }
 
 #calculate confidence bound for Transfer Entropy statistical significance
-tr_confidence <- function(x, y, runs = 1000) {
+tr_confidence <- function(x, y, xlag, ylag = 1, runs = 1000, bins = 10, normalize = T) {
   
   mc_out <- rep(NA, runs) #vector for statistic output
   
   for (i in 1:runs) {
     
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
-    mc_out[i] <- transfer_entropy(rand_x, y, normalize = T) #calculate MI between shuffled x and y
+    mc_out[i] <- transfer_entropy(rand_x, y, xlag, ylag, bins = bins, normalize = normalize)
   }
   mean(mc_out)
 }
 
-#calculate times series of Monte Carlo limits
-conf_series <- function(x, y, data_list, runs = 1000, type=c("I", "T")) {
+#calculate times series of Monte Carlo limits (does not include time lags)
+conf_series <- function(x, y, data_list, runs = 1000, type=c("MI", "TR")) {
   
   MC_series <- vector("double", nrow(data_list))
   
@@ -37,9 +37,9 @@ conf_series <- function(x, y, data_list, runs = 1000, type=c("I", "T")) {
     x_var <- eval(substitute(x), current_df)
     y_var <- eval(substitute(y), current_df)
     
-    if (type == "I") {
+    if (type == "MI") {
       MC_mean <- mi_confidence(x_var, y_var, runs)
-    } else if (type == "T") {
+    } else if (type == "TR") {
[…]

### 2018-04-02 R/testing.R

@@ -1,0 +1,20 @@
+anom_filter <- function(var, window = 7) {
+  as.numeric(var - ma(var, order = window))
+}
+
+test <- subset(peat6_all, year == 2016 & DOY > 100 & DOY < 300)
+
+anom_data <- test %>%
+  arrange(time) %>%
+  mutate(CH4_anom = anom_filter(wm_gf),
+         TA_anom = anom_filter(TA.x),
+         GPP_anom = anom_filter(gpp_ANNnight)) %>%
+  arrange(datetime)
+
+tr_wm_TA <- lag_tr(test$gpp_ANNnight, test$wm_gf, 48*2, normalize = T)
+conf_wm_TA <- lag_confidence(test$gpp_ANNnight, test$wm_gf, 48*2, type = "TR", runs = 10)
+
+Hours <- seq(0.5, 24*2, by = 0.5)
+
+plot(tr_wm_TA ~ Hours, type = "l", xlim = c(0,36), col = "red")
+points(conf_wm_TA*1.66 ~ Hours, type = "l")

### 2018-04-04 R/TR_functions.R
some TR analysis, improving significance tests

@@ -57,7 +57,6 @@ lag_tr <- function(x, y, lags, bins = 10, normalize = TRUE) {
 tr_timeseries <- function(x, y, data_list, lags, bins = 10, normalize = TRUE, type = c("observed", "shuffled")) {
   
   output_list <- list()
-  #tr_series <- data.frame("double", ncol(data_list), nrow(lags)) #vector to store transfer entropy
   
   #iterate through indexed datasets and calculate Tr
   for (i in 1:nrow(data_list)) {
@@ -72,7 +71,7 @@ tr_timeseries <- function(x, y, data_list, lags, bins = 10, normalize = TRUE, ty
     if (type == "observed") {
       output_list[[name]] <- lag_tr(x_var, y_var, lags, bins, normalize)
     } else if (type == "shuffled") {
-      output_list[[name]] <- lag_confidence(x_var, y_var, lags, type = "TR", runs = 10, bins, normalize)
+      output_list[[name]] <- lag_confidence(x_var, y_var, alpha = 0.01, lags, type = "TR", runs = 10, bins, normalize)
     } else {
       print("Warning: type not assigned correctly")
     }

### 2018-04-04 R/signficance_tests.R

@@ -15,7 +15,7 @@ mi_confidence <- function(x, y, runs = 1000, bins = 10, normalize = T) {
 }
 
 #calculate confidence bound for Transfer Entropy statistical significance
-tr_confidence <- function(x, y, xlag, ylag = 1, runs = 1000, bins = 10, normalize = T) {
+tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 1000, bins = 10, normalize = T) {
   
   mc_out <- rep(NA, runs) #vector for statistic output
   
@@ -24,7 +24,15 @@ tr_confidence <- function(x, y, xlag, ylag = 1, runs = 1000, bins = 10, normaliz
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
     mc_out[i] <- transfer_entropy(rand_x, y, xlag, ylag, bins = bins, normalize = normalize)
   }
-  mean(mc_out)
+  
+  if (alpha == 0.01) {
+    limit <- mean(mc_out) + 2.36*sd(mc_out)
+  } else if (alpha == 0.05) {
+    limit <- mean(mc_out) + 1.66*sd(mc_out)
+  } else {
+    return("This threshold is not supported")
+  }
+  limit
 }
 
 #calculate times series of Monte Carlo limits (does not include time lags)
@@ -50,7 +58,8 @@ conf_series <- function(x, y, data_list, runs = 1000, type=c("MI", "TR")) {
   MC_series
 }
 
-lag_confidence <- function(x, y, lags, type = c("MI", "TR"), runs = 1000, bins = 10, normalize = TRUE) {
+lag_confidence <- function(x, y, lags, type = c("MI", "TR"), alpha, 
+                           runs = 1000, bins = 10, normalize = TRUE) {
   
   MC_lagseries <- vector("double", lags) #vector for shuffled metrics
   
@@ -61,7 +70,7 @@ lag_confidence <- function(x, y, lags, type = c("MI", "TR"), runs = 1000, bins =
     }
   } else if (type == "TR") {
     for (i in 1:(lags)) {
-      MC_lagseries[[i]] <- tr_confidence(x, y, xlag = i, runs = runs, bins = bins, normalize = normalize)
+      MC_lagseries[[i]] <- tr_confidence(x, y, xlag = i, ylag = 1, alpha, runs, bins, normalize)
     }
   } else {
     return("Warning: not a valid test")

### 2018-04-04 R/testing.R

@@ -1,20 +1,23 @@
-anom_filter <- function(var, window = 7) {
+anom_filter <- function(var, window = 5) {
   as.numeric(var - ma(var, order = window))
 }
 
-test <- subset(peat6_all, year == 2016 & DOY > 100 & DOY < 300)
+test <- subset(peat6_all, year == 2012 & DOY > 100 & DOY < 300)
 
-anom_data <- test %>%
+test <- test %>%
   arrange(time) %>%
   mutate(CH4_anom = anom_filter(wm_gf),
          TA_anom = anom_filter(TA.x),
          GPP_anom = anom_filter(gpp_ANNnight)) %>%
   arrange(datetime)
 
-tr_wm_TA <- lag_tr(test$gpp_ANNnight, test$wm_gf, 48*2, normalize = T)
-conf_wm_TA <- lag_confidence(test$gpp_ANNnight, test$wm_gf, 48*2, type = "TR", runs = 10)
+#re-insert NA values to CH4 anomaly
+test$CH4na_anom <- ifelse(is.na(test$wm), NA, test$CH4_anom)
+
+tr_wm_TA <- lag_tr(test$GPP_anom, test$CH4na_anom, 48*2, normalize = T)
+conf_wm_TA <- lag_confidence(test$GPP_anom, test$CH4na_anom, 48*2, type = "TR", alpha = 0.05, runs = 20)
 
 Hours <- seq(0.5, 24*2, by = 0.5)
 
-plot(tr_wm_TA ~ Hours, type = "l", xlim = c(0,36), col = "red")
-points(conf_wm_TA*1.66 ~ Hours, type = "l")
+plot(tr_wm_TA ~ Hours, type = "l", xlim = c(0,36), col = "black")
+points(conf_wm_TA ~ Hours, type = "l", col = "red")

### 2018-04-06 R/TR_functions.R
Strong improvement to MI and TR figures and tweaks to function library

@@ -54,7 +54,7 @@ lag_tr <- function(x, y, lags, bins = 10, normalize = TRUE) {
 }
 
 #calculate Tr time series based on data in list form grouped by time index
-tr_timeseries <- function(x, y, data_list, lags, bins = 10, normalize = TRUE, type = c("observed", "shuffled")) {
+tr_timeseries <- function(x, y, data_list, lags, runs, bins = 10, alpha = 0.05, normalize = TRUE, type = c("observed", "shuffled")) {
   
   output_list <- list()
   
@@ -71,7 +71,7 @@ tr_timeseries <- function(x, y, data_list, lags, bins = 10, normalize = TRUE, ty
     if (type == "observed") {
       output_list[[name]] <- lag_tr(x_var, y_var, lags, bins, normalize)
     } else if (type == "shuffled") {
-      output_list[[name]] <- lag_confidence(x_var, y_var, alpha = 0.01, lags, type = "TR", runs = 10, bins, normalize)
+      output_list[[name]] <- lag_confidence(x_var, y_var, lags, type = "TR", alpha, runs, bins, normalize)
     } else {
       print("Warning: type not assigned correctly")
     }

### 2018-04-06 R/new_functions.R

@@ -1,3 +1,15 @@
+#' Misc functions for data and list transformations:
+#' anom_filter - removes periodic signal from data
+#' 
+#'
+#' @importFrom dplyr lag
+
+anom_filter <- function(var, window = 5) {
+  as.numeric(var - ma(var, order = window))
+}
+
+
+
 joint_entropy <- function(x, y, bins = 11) {
   
   clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables

### 2018-04-06 R/signficance_tests.R

@@ -1,17 +1,26 @@
 #' Functions for statistical signficance of mutual information and transfer entropy via
 #' Monte Carlo reshuffling of datasets. Includes functions for single test and time series
+#'
+#' @importFrom dplyr lag
 
 #calculate confidence bound for Mutual Information statistical significance
-mi_confidence <- function(x, y, runs = 1000, bins = 10, normalize = T) {
+mi_confidence <- function(x, y, alpha = 0.05, runs = 1000, bins = 10, normalize = T) {
   
   mc_out <- rep(NA, runs) #vector for statistic output
   
   for (i in 1:runs) {
-    
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
-    mc_out[i] <- mutual_info(rand_x, y, bins = bins, normalize = normalize) #calculate MI between shuffled x and y
+    mc_out[i] <- mutual_info(rand_x, y, bins, normalize) #calculate MI between shuffled x and y
   }
-  mean(mc_out)
+  
+  if (alpha == 0.01) {
+    limit <- mean(mc_out) + 2.36*sd(mc_out)
+  } else if (alpha == 0.05) {
+    limit <- mean(mc_out) + 1.66*sd(mc_out)
+  } else {
+    return("This threshold is not supported")
+  }
+  limit
 }
 
 #calculate confidence bound for Transfer Entropy statistical significance
@@ -20,7 +29,6 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 1000, bins = 10, n
   mc_out <- rep(NA, runs) #vector for statistic output
   
   for (i in 1:runs) {
-    
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
     mc_out[i] <- transfer_entropy(rand_x, y, xlag, ylag, bins = bins, normalize = normalize)
   }
@@ -36,7 +44,7 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 1000, bins = 10, n
 }
 
 #calculate times series of Monte Carlo limits (does not include time lags)
-conf_series <- function(x, y, data_list, runs = 1000, type=c("MI", "TR")) {
+conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, type=c("MI", "TR")) {
   
   MC_series <- vector("double", nrow(data_list))
   
[…]

### 2018-04-06 R/transformations.R

@@ -1,0 +1,67 @@
+#' Misc functions for data and list transformations:
+#' anom_filter - removes periodic signal from data
+#' 
+#'
+#' @importFrom dplyr lag
+#' @importFrom tidyr gather
+#' @importFrom stringr str_replace
+#' @importFrom purrr map_df
+
+anom_filter <- function(var, window = 5) {
+  as.numeric(var - ma(var, order = window))
+}
+
+tidy_list <- function(list) {
+  
+  df <- as.data.frame(list)
+  df$lag <- rownames(df) #rownames correspond to lag
+  df <- gather(df, year, tr, -lag) #tidy with year by lag
+  df$year <- str_replace(df$year, 'X', '') #clean up year column
+  df <- map_df(df, as.numeric) #make all columns numeric
+  df$hour <- df$lag/2
+  
+  #create year index that also displays mean annual conductivity
+  
+  return(df)
+}
+
+# joint_entropy <- function(x, y, bins = 11) {
+#   
+#   clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables
+#   r1 = range(clip_set$x); r2 = range(clip_set$y)
+#   
+#   # bin label for every observation of x and y
+#   x_breaks <- seq(from=r1[1], to=r1[2], length.out=bins+1)
+#   y_breaks <- seq(from=r2[1], to=r2[2], length.out=bins+1)
+#   
+#   #create vector of bin assignments
+#   x_bin <- table(cut(clip_set$x, x_breaks, include.lowest = T, labels = 1:bins))
+#   y_bin <- table(cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins))
+#   
+#   #calculate joint and marginal entropies
+#   p_x <- x_bin/sum(x_bin)
+#   p_y <- y_bin/sum(y_bin)
+#   
+#   -sum(p_y[p_y > 0]*log(p_y[p_y > 0]))
+#   double <- table(cut(clip_set$x, x_breaks, include.lowest = T, labels = 1:bins), 
+#                   cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins),
+#                   cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins))
+#   
+#   double
+#   #p_double <- double/sum(double)
+#   #-sum(p_double[p_double > 0]*log(p_double[p_double > 0]))
+#   
+# }
+# 
[…]

### 2018-04-08 R/TR_functions.R
Two additional figures, getting close to a complete manuscript minus water chemistry parts

@@ -20,7 +20,7 @@ transfer_entropy <- function(x, y, xlag, ylag = 1, bins = 10, normalize = TRUE) 
   Hy <- entropy.empirical(discretize(na.omit(clip_set$y), numBins = bins), unit = "log2") # entropy at current state
   
   if (normalize == T) {
-    Tr = (Hxy + Hyy - Hyl - Hxyz)/Hy
+    Tr = (Hxy + Hyy - Hyl - Hxyz)/Hyl
   } else {
     Tr = Hxy + Hyy - Hyl - Hxyz
   }

### 2018-04-13 R/signficance_tests.R
Updates to sig levels for 25 MCs

@@ -4,7 +4,7 @@
 #' @importFrom dplyr lag
 
 #calculate confidence bound for Mutual Information statistical significance
-mi_confidence <- function(x, y, alpha = 0.05, runs = 1000, bins = 10, normalize = T) {
+mi_confidence <- function(x, y, alpha = 0.05, runs = 100, bins = 10, normalize = T) {
   
   mc_out <- rep(NA, runs) #vector for statistic output
   
@@ -24,7 +24,7 @@ mi_confidence <- function(x, y, alpha = 0.05, runs = 1000, bins = 10, normalize 
 }
 
 #calculate confidence bound for Transfer Entropy statistical significance
-tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 1000, bins = 10, normalize = T) {
+tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 25, bins = 10, normalize = T) {
   
   mc_out <- rep(NA, runs) #vector for statistic output
   
@@ -34,9 +34,9 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 1000, bins = 10, n
   }
   
   if (alpha == 0.01) {
-    limit <- mean(mc_out) + 2.36*sd(mc_out)
+    limit <- mean(mc_out) + 2.49*sd(mc_out)
   } else if (alpha == 0.05) {
-    limit <- mean(mc_out) + 1.66*sd(mc_out)
+    limit <- mean(mc_out) + 1.71*sd(mc_out)
   } else {
     return("This threshold is not supported")
   }

### 2018-04-18 R/peat19_processing.R
mostly completed methods and results, moved come figures to supplement, addition of salinity calculations

@@ -5,11 +5,13 @@
 #' @import dplyr
 #' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
+#' @importFrom wq ec2pss
 
 # load eddy flux and met dataset
 load("data/peat19_all.Rdata")
 peat19_all$dday <- floor(peat19_all$decday)
-peat19_all$site <- "Mature"
+peat19_all$site <- "Baseline (mature)"
+peat19_all$sal <- ec2pss(peat19_all$conductivity, peat19_all$TW_8cm)
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat19_all %>%
@@ -38,6 +40,7 @@ daily <- peat19_all %>%
             Rain = 1,
             WTD = mean(WT, na.rm=T),    #water table (m from surface)
             Cond = mean(conductivity, na.rm=T), #conductivity (mS)
+            Sal = mean(sal, na.rm=T),          #salinity (psu)
             t_obs = length(wc_gf),      # total observations in the day
             year = round(median(year))) %>%
   filter(t_obs == 48 & year > 2012)  #remove incomplete days at either end of time series and year with water table drop issues
@@ -59,7 +62,7 @@ monthly <- daily %>%
             mER = mean(gER),
             mGEP = mean(gGEP),
             mCond = mean(Cond, na.rm=T),
-            #mSal = mean(Sal, na.rm=T),
+            mSal = mean(Sal, na.rm=T),
             datetime = mean(datetime),
             days = sum(!is.na(mgCH4)),
             CH4_obs = sum(m_obs),

### 2018-04-18 R/peat6_processing.R

@@ -5,10 +5,13 @@
 #' @import dplyr
 #' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
+#' @importFrom wq ec2pss
 
 # load eddy flux and met dataset
 load("data/peat6_all.Rdata")
 peat6_all$dday <- floor(peat6_all$decday)
+peat6_all$sal <- ec2pss(peat6_all$Cond, peat6_all$TW_TULE_10cm)
+peat6_all$site <- 'Salinity rise'
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%
@@ -37,14 +40,15 @@ daily <- peat6_all %>%
             Rain = sum(PRECIP, na.rm=T),       #rain (mm)
             WTD = mean(WT, na.rm=T),           #water table (m from surface)
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
-            DOrange1 = max(DO_mid, na.rm=T) - min(DO_mid, na.rm=T),
-            DOmid = mean(DO_mid, na.rm=T),
-            DOrange2 = max(DO_deep, na.rm=T) - min(DO_deep, na.rm=T),
-            DOdiff = mean(DO_mid, na.rm=T) - mean(DO_deep, na.rm=T),
-            COrangeS = max(wCO2_open_surface_ppm, na.rm=T) - min(wCO2_open_surface_ppm, na.rm=T),
-            COrangeM = max(wCO2_open_mid_ppm, na.rm=T) - min(wCO2_open_mid_ppm, na.rm=T),
-            COrangeD = max(wCO2_open_deep_ppm, na.rm=T) - min(wCO2_open_deep_ppm, na.rm=T),
-            COdiff = mean(wCO2_open_surface_ppm, na.rm=T) - mean(wCO2_open_deep_ppm, na.rm=T),
+            Sal = mean(sal, na.rm=T),          #salinity (psu)
+            # DOrange1 = max(DO_mid, na.rm=T) - min(DO_mid, na.rm=T),
+            # DOmid = mean(DO_mid, na.rm=T),
+            # DOrange2 = max(DO_deep, na.rm=T) - min(DO_deep, na.rm=T),
+            # DOdiff = mean(DO_mid, na.rm=T) - mean(DO_deep, na.rm=T),
+            # COrangeS = max(wCO2_open_surface_ppm, na.rm=T) - min(wCO2_open_surface_ppm, na.rm=T),
[…]

### 2018-04-23 R/MI_functions.R
Discussion writing and updates to Supplement Materials

@@ -10,17 +10,17 @@ mutual_info <- function(x, y, bins = 10, normalize = TRUE) {
   clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables
 
   y2d <- discretize2d(clip_set$x, clip_set$y, numBins1 = bins, numBins2 = bins) #joint distribution
-  
+
   Hx <- entropy.empirical(rowSums(y2d)) #entropy x variable
   Hy <- entropy.empirical(colSums(y2d)) #entropy y variable
   Hxy <- entropy.empirical(y2d) #joint entropy
-  
+
   if (normalize == T) {
     I <- (Hx + Hy - Hxy)/Hy #relative mutual information
   } else {
     I <- (Hx + Hy - Hxy) #absolute mutual information
   }
-  
+
   return(I)
 }
 
@@ -55,7 +55,7 @@ mi_timeseries <- function(x, y, data_list, bins = 10, normalize = TRUE) {
 }
 
 #calculate correlation coefficients for comparison
-corr_timeseries <- function(x, y, data_list, method = "pearson") {
+corr_timeseries <- function(x, y, data_list) {
 
   corr_series <- vector("double", nrow(data_list)) #vector to store correlation coefficients
 
@@ -65,7 +65,7 @@ corr_timeseries <- function(x, y, data_list, method = "pearson") {
     x_var <- eval(substitute(x), current_df)
     y_var <- eval(substitute(y), current_df)
 
-    out <- cor.test(x_var, y_var, method = method)
+    out <- cor.test(x_var, y_var, method = "kendall")
     corr_series[[i]] <- out$estimate[[1]]
   }
   corr_series

### 2018-04-28 R/signficance_tests.R
Turn off messages

@@ -5,14 +5,14 @@
 
 #calculate confidence bound for Mutual Information statistical significance
 mi_confidence <- function(x, y, alpha = 0.05, runs = 100, bins = 10, normalize = T) {
-  
+
   mc_out <- rep(NA, runs) #vector for statistic output
-  
+
   for (i in 1:runs) {
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
     mc_out[i] <- mutual_info(rand_x, y, bins, normalize) #calculate MI between shuffled x and y
   }
-  
+
   if (alpha == 0.01) {
     limit <- mean(mc_out) + 2.36*sd(mc_out)
   } else if (alpha == 0.05) {
@@ -25,14 +25,14 @@ mi_confidence <- function(x, y, alpha = 0.05, runs = 100, bins = 10, normalize =
 
 #calculate confidence bound for Transfer Entropy statistical significance
 tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 25, bins = 10, normalize = T) {
-  
+
   mc_out <- rep(NA, runs) #vector for statistic output
-  
+
   for (i in 1:runs) {
     rand_x <- sample(x, length(x), replace = F) #randomly shuffle x variable
     mc_out[i] <- transfer_entropy(rand_x, y, xlag, ylag, bins = bins, normalize = normalize)
   }
-  
+
   if (alpha == 0.01) {
     limit <- mean(mc_out) + 2.49*sd(mc_out)
   } else if (alpha == 0.05) {
@@ -45,14 +45,14 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 25, bins = 10, nor
 
 #calculate times series of Monte Carlo limits (does not include time lags)
 conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, type=c("MI", "TR")) {
-  
+
   MC_series <- vector("double", nrow(data_list))
-  
+
   for (i in 1:nrow(data_list)) {
     current_df <- data_list$data[[i]]
     x_var <- eval(substitute(x), current_df)
     y_var <- eval(substitute(y), current_df)
-    
+
     if (type == "MI") {
       MC_mean <- mi_confidence(x_var, y_var, alpha, runs)
     } else if (type == "TR") {
@@ -60,17 +60,17 @@ conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, type=c("MI",
     } else {
[…]

### 2018-04-30 R/scratch.R
move to percentile MC

@@ -1,0 +1,49 @@
+#add this to the supplement.....
+
+#apply anomaly filter
+anom_data <- peat6_all %>%
+  arrange(year, time) %>%
+  mutate(CH4_anom = anom_filter(wm_gf),
+         TA_anom = anom_filter(TA.x),
+         GPP_anom = anom_filter(gpp_ANNnight))
+
+anom_data <- arrange(anom_data, datetime)
+anom_data$CH4na_anom <- ifelse(is.na(anom_data$wm), NA, anom_data$CH4_anom) # re-insert missing values
+
+#create data list by annual growing season
+by_year <- anom_data %>%
+  filter(DOY > 100 & DOY < 300 & year == 2012)
+
+#calculate lagged transfer entropy time series (up to 2 day lag at half-hourly timestep)
+# for GPP -> CH4
+tr_wm_gpp <- transfer_entropy(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1)
+
+bin_tests <- rep(seq(10, 100, by = 10), each = 3)
+high_bins <- rep(c(500, 1000), each = 10)
+bin_tests <- c(bin_tests, high_bins)
+output <- rep(NA, length(bin_tests))
+
+for (i in 1:length(bin_tests)) {
+  output[i] <- tr_confidence(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1, alpha = 0.05,
+                             bins = 10, runs = bin_tests[i])
+}
+
+output_set <- data.frame(output, bin_tests)
+
+ggplot(output_set, aes(x = bin_tests, y = output)) +
+  geom_point() +
+  stat_smooth(se = FALSE)
+
+sig_limits <- rep(seq(0.01, .1, by = 0.01), each = 10)
+output <- rep(NA, length(sig_limits))
+
+for (i in 1:length(sig_limits)) {
+  output[i] <- tr_confidence(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1, alpha = sig_limits[i],
+                             bins = 10, runs = 25)
+}
+
+output_set <- data.frame(output, sig_limits)
+
+ggplot(output_set, aes(x = sig_limits, y = output)) +
+  geom_point() +
+  stat_smooth(se = FALSE)

### 2018-04-30 R/signficance_tests.R

@@ -13,18 +13,24 @@ mi_confidence <- function(x, y, alpha = 0.05, runs = 100, bins = 10, normalize =
     mc_out[i] <- mutual_info(rand_x, y, bins, normalize) #calculate MI between shuffled x and y
   }
 
-  if (alpha == 0.01) {
-    limit <- mean(mc_out) + 2.36*sd(mc_out)
-  } else if (alpha == 0.05) {
-    limit <- mean(mc_out) + 1.66*sd(mc_out)
+  if (alpha > 0 && alpha < 1) {
+    limit <- quantile(mc_out, probs = (1 - alpha))[[1]]
   } else {
-    return("This threshold is not supported")
+    return("Error: sig. limit out of range (0 - 1).")
   }
+
+  # if (alpha == 0.01) {
+  #   limit <- mean(mc_out) + 2.36*sd(mc_out)
+  # } else if (alpha == 0.05) {
+  #   limit <- mean(mc_out) + 1.66*sd(mc_out)
+  # } else {
+  #   return("This threshold is not supported")
+  # }
   limit
 }
 
 #calculate confidence bound for Transfer Entropy statistical significance
-tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 25, bins = 10, normalize = T) {
+tr_confidence <- function(x, y, xlag, ylag = 1, alpha = 0.05, runs = 25, bins = 10, normalize = T) {
 
   mc_out <- rep(NA, runs) #vector for statistic output
 
@@ -33,13 +39,19 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha, runs = 25, bins = 10, nor
     mc_out[i] <- transfer_entropy(rand_x, y, xlag, ylag, bins = bins, normalize = normalize)
   }
 
-  if (alpha == 0.01) {
-    limit <- mean(mc_out) + 2.49*sd(mc_out)
-  } else if (alpha == 0.05) {
-    limit <- mean(mc_out) + 1.71*sd(mc_out)
+  if (alpha > 0 && alpha < 1) {
+    limit <- quantile(mc_out, probs = (1 - alpha))[[1]]
   } else {
-    return("This threshold is not supported")
+    return("Error: sig. limit out of range (0 - 1).")
   }
+  # if (alpha == 0.01) {
+  #   limit <- mean(mc_out) + 2.49*sd(mc_out)
+  # } else if (alpha == 0.05) {
[…]

### 2018-04-30 R/TR_functions.R
some clarity updates to functions

@@ -5,20 +5,20 @@
 #' @importFrom dplyr lag
 
 transfer_entropy <- function(x, y, xlag, ylag = 1, bins = 10, normalize = TRUE) {
-  
+
   x_lag <- dplyr::lag(x, n = xlag)
   y_lag <- dplyr::lag(y, n = ylag)
-  
+
   #clip_set <- data.frame(x_lag, y_lag, y)
   #clip_set[!complete.cases(clip_set), ] <- NA #this follows Laurel and Ben's code
   clip_set <- na.omit(data.frame(x_lag, y_lag, y)) #clip rows were any value is missing
-  
+
   Hxy <- entropy.empirical(discretize2d(clip_set$x_lag, clip_set$y_lag, numBins1 = bins, numBins2 = bins), unit = "log2")
   Hyy <- entropy.empirical(discretize2d(clip_set$y, clip_set$y_lag,  numBins1 = bins, numBins2 = bins), unit = "log2")
   Hyl <- entropy.empirical(discretize(na.omit(clip_set$y_lag), numBins = bins), unit = "log2")
   Hxyz <- entropy.empirical(discretize3d(clip_set$x_lag, clip_set$y_lag, clip_set$y, numBins = bins), unit = "log2")
   Hy <- entropy.empirical(discretize(na.omit(clip_set$y), numBins = bins), unit = "log2") # entropy at current state
-  
+
   if (normalize == T) {
     Tr = (Hxy + Hyy - Hyl - Hxyz)/Hyl
   } else {
@@ -33,47 +33,47 @@ discretize3d = function( x1, x2, x3, numBins, r1=range(x1), r2=range(x2), r3=ran
   b1 = seq(from = r1[1], to = r1[2], length.out = numBins+1)
   b2 = seq(from = r2[1], to = r2[2], length.out = numBins+1)
   b3 = seq(from = r3[1], to = r3[2], length.out = numBins+1)
-  
-  y3d = table( cut(x1, breaks=b1, include.lowest=TRUE ), 
+
+  y3d = table( cut(x1, breaks=b1, include.lowest=TRUE ),
                cut(x2, breaks=b2, include.lowest=TRUE ),
                cut(x3, breaks=b3, include.lowest=TRUE ))
-  
+
   return( y3d )
 }
 
 #calculate Tr at multiple lags of x variable
 lag_tr <- function(x, y, lags, bins = 10, normalize = TRUE) {
-  
+
[…]

### 2018-04-30 R/scratch.R

@@ -10,27 +10,23 @@ anom_data <- peat6_all %>%
 anom_data <- arrange(anom_data, datetime)
 anom_data$CH4na_anom <- ifelse(is.na(anom_data$wm), NA, anom_data$CH4_anom) # re-insert missing values
 
-#create data list by annual growing season
-by_year <- anom_data %>%
-  filter(DOY > 100 & DOY < 300 & year == 2012)
-
 #calculate lagged transfer entropy time series (up to 2 day lag at half-hourly timestep)
 # for GPP -> CH4
 tr_wm_gpp <- transfer_entropy(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1)
 
-bin_tests <- rep(seq(10, 100, by = 10), each = 3)
-high_bins <- rep(c(500, 1000), each = 10)
-bin_tests <- c(bin_tests, high_bins)
-output <- rep(NA, length(bin_tests))
+run_tests <- rep(seq(10, 100, by = 10), each = 5)
+high_runs <- rep(c(500, 1000), each = 5)
+run_tests <- c(run_tests, high_runs)
+output <- rep(NA, length(run_tests))
 
-for (i in 1:length(bin_tests)) {
+for (i in 1:length(run_tests)) {
   output[i] <- tr_confidence(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1, alpha = 0.05,
-                             bins = 10, runs = bin_tests[i])
+                             bins = 10, runs = run_tests[i])
 }
 
-output_set <- data.frame(output, bin_tests)
+output_set <- data.frame(output, run_tests)
 
-ggplot(output_set, aes(x = bin_tests, y = output)) +
+ggplot(output_set, aes(x = run_tests, y = output)) +
   geom_point() +
   stat_smooth(se = FALSE)
 

### 2018-04-30 R/signficance_tests.R

@@ -56,7 +56,7 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha = 0.05, runs = 25, bins = 
 }
 
 #calculate times series of Monte Carlo limits (does not include time lags)
-conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, type=c("MI", "TR")) {
+conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, bins = 10, type=c("MI", "TR")) {
 
   MC_series <- vector("double", nrow(data_list))
 
@@ -66,9 +66,9 @@ conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, type=c("MI",
     y_var <- eval(substitute(y), current_df)
 
     if (type == "MI") {
-      MC_mean <- mi_confidence(x_var, y_var, alpha, runs)
+      MC_mean <- mi_confidence(x_var, y_var, alpha, runs, bins)
     } else if (type == "TR") {
-      MC_mean <- tr_confidence(x_var, y_var, alpha, runs)
+      MC_mean <- tr_confidence(x_var, y_var, alpha, runs, bins)
     } else {
       return("Warning: not a valid test")
     }
@@ -86,7 +86,7 @@ lag_confidence <- function(x, y, lags, type = c("MI", "TR"), alpha,
   if (type == "MI") {
     for (i in 1:(lags + 1)) {
       x_lag <- dplyr::lag(x, n = i-1) # include syncronhous interactions
-      MC_lagseries[[i]] <- mi_confidence(xlag, y, runs = runs, bins = bins, normalize = normalize)
+      MC_lagseries[[i]] <- mi_confidence(xlag, y, alpha, runs, bins, normalize)
     }
   } else if (type == "TR") {
     for (i in 1:(lags)) {

### 2018-05-03 R/scratch.R
minor updates so not dependent on environment

@@ -10,12 +10,14 @@ anom_data <- peat6_all %>%
 anom_data <- arrange(anom_data, datetime)
 anom_data$CH4na_anom <- ifelse(is.na(anom_data$wm), NA, anom_data$CH4_anom) # re-insert missing values
 
+by_year <- subset(anom_data, year == 2012 & DOY > 100 & DOY < 300)
+
 #calculate lagged transfer entropy time series (up to 2 day lag at half-hourly timestep)
 # for GPP -> CH4
 tr_wm_gpp <- transfer_entropy(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1)
 
-run_tests <- rep(seq(10, 100, by = 10), each = 5)
-high_runs <- rep(c(500, 1000), each = 5)
+run_tests <- rep(seq(10, 100, by = 10), each = 10)
+high_runs <- rep(c(250, 500, 1000), each = 10)
 run_tests <- c(run_tests, high_runs)
 output <- rep(NA, length(run_tests))
 
@@ -28,6 +30,7 @@ output_set <- data.frame(output, run_tests)
 
 ggplot(output_set, aes(x = run_tests, y = output)) +
   geom_point() +
+  xlab("Num. of runs") + ylab("TE limit") +
   stat_smooth(se = FALSE)
 
 sig_limits <- rep(seq(0.01, .1, by = 0.01), each = 10)

### 2018-06-04 README.Rmd
start of work on built check fixes, still need to add documentation for functions and tests

@@
 
-The goal of salinity is to ...
+This package was used the generate the manuscript "Effect of drought-induced salinization on wetland methane emissions, gross
+  ecosystem photosynthesis, and their interactions." by Samuel D.
+Chamberlain et.
+al.
+The /data folder contains half-hourly eddy covariance files used in the analysis, the /R folder contains scripts used to process data and information theory functions, and the /vignettes folder contains the Markdown and bibiography files used to generate the manuscript.
 
-## Example
+## Installation
 
-This is a basic example which shows you how to solve a common problem:
+You can install salinity from github with:
 
-```{r example}
-## basic example code
+```{r gh-installation, eval = FALSE}
+# install.packages("devtools")
+devtools::install_github("samdchamberlain/salinity")
 ```
+
+## How to Run
+Load package into RStudio and open the 'manuscript.Rmd' within the /vignettes folder.
+Using RStudio, click the 'Knit' button at the top of the console and this manuscript, and analyses herein, will be re-created.

### 2018-06-04 R/new_functions.R

@@ -1,52 +1,0 @@
-#' Misc functions for data and list transformations:
-#' anom_filter - removes periodic signal from data
-#' 
-#'
-#' @importFrom dplyr lag
-
-anom_filter <- function(var, window = 5) {
-  as.numeric(var - ma(var, order = window))
-}
-
-
-
-joint_entropy <- function(x, y, bins = 11) {
-  
-  clip_set <- na.omit(data.frame(x, y)) #clear NA values from x,y variables
-  r1 = range(clip_set$x); r2 = range(clip_set$y)
-  
-  # bin label for every observation of x and y
-  x_breaks <- seq(from=r1[1], to=r1[2], length.out=bins+1)
-  y_breaks <- seq(from=r2[1], to=r2[2], length.out=bins+1)
-  
-  #create vector of bin assignments
-  x_bin <- table(cut(clip_set$x, x_breaks, include.lowest = T, labels = 1:bins))
-  y_bin <- table(cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins))
-  
-  #calculate joint and marginal entropies
-  p_x <- x_bin/sum(x_bin)
-  p_y <- y_bin/sum(y_bin)
-  
-  -sum(p_y[p_y > 0]*log(p_y[p_y > 0]))
-  double <- table(cut(clip_set$x, x_breaks, include.lowest = T, labels = 1:bins), 
-                  cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins),
-                  cut(clip_set$y, y_breaks, include.lowest = T, labels = 1:bins))
-  
-  double
-  #p_double <- double/sum(double)
-  #-sum(p_double[p_double > 0]*log(p_double[p_double > 0]))
-  
-}
-
-discretize3d = function( x1, x2, x3, numBins, r1=range(x1), r2=range(x2), r3=range(x3))
-  {
-  b1 = seq(from = r1[1], to = r1[2], length.out = numBins+1)
-  b2 = seq(from = r2[1], to = r2[2], length.out = numBins+1)
-  b3 = seq(from = r3[1], to = r3[2], length.out = numBins+1)
-  
-  y3d = table( cut(x1, breaks=b1, include.lowest=TRUE ), 
-               cut(x2, breaks=b2, include.lowest=TRUE ),
-               cut(x3, breaks=b3, include.lowest=TRUE ))
-  
-  return( y3d )
-}

### 2018-06-04 R/scratch.R

@@ -1,48 +1,0 @@
-#add this to the supplement.....
-
-#apply anomaly filter
-anom_data <- peat6_all %>%
-  arrange(year, time) %>%
-  mutate(CH4_anom = anom_filter(wm_gf),
-         TA_anom = anom_filter(TA.x),
-         GPP_anom = anom_filter(gpp_ANNnight))
-
-anom_data <- arrange(anom_data, datetime)
-anom_data$CH4na_anom <- ifelse(is.na(anom_data$wm), NA, anom_data$CH4_anom) # re-insert missing values
-
-by_year <- subset(anom_data, year == 2012 & DOY > 100 & DOY < 300)
-
-#calculate lagged transfer entropy time series (up to 2 day lag at half-hourly timestep)
-# for GPP -> CH4
-tr_wm_gpp <- transfer_entropy(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1)
-
-run_tests <- rep(seq(10, 100, by = 10), each = 10)
-high_runs <- rep(c(250, 500, 1000), each = 10)
-run_tests <- c(run_tests, high_runs)
-output <- rep(NA, length(run_tests))
-
-for (i in 1:length(run_tests)) {
-  output[i] <- tr_confidence(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1, alpha = 0.05,
-                             bins = 10, runs = run_tests[i])
-}
-
-output_set <- data.frame(output, run_tests)
-
-ggplot(output_set, aes(x = run_tests, y = output)) +
-  geom_point() +
-  xlab("Num. of runs") + ylab("TE limit") +
-  stat_smooth(se = FALSE)
-
-sig_limits <- rep(seq(0.01, .1, by = 0.01), each = 10)
-output <- rep(NA, length(sig_limits))
-
-for (i in 1:length(sig_limits)) {
-  output[i] <- tr_confidence(by_year$GPP_anom, by_year$CH4na_anom, xlag = 1, alpha = sig_limits[i],
-                             bins = 10, runs = 25)
-}
-
-output_set <- data.frame(output, sig_limits)
-
-ggplot(output_set, aes(x = sig_limits, y = output)) +
-  geom_point() +
-  stat_smooth(se = FALSE)

### 2018-06-04 R/testing.R

@@ -1,23 +1,0 @@
-anom_filter <- function(var, window = 5) {
-  as.numeric(var - ma(var, order = window))
-}
-
-test <- subset(peat6_all, year == 2012 & DOY > 100 & DOY < 300)
-
-test <- test %>%
-  arrange(time) %>%
-  mutate(CH4_anom = anom_filter(wm_gf),
-         TA_anom = anom_filter(TA.x),
-         GPP_anom = anom_filter(gpp_ANNnight)) %>%
-  arrange(datetime)
-
-#re-insert NA values to CH4 anomaly
-test$CH4na_anom <- ifelse(is.na(test$wm), NA, test$CH4_anom)
-
-tr_wm_TA <- lag_tr(test$GPP_anom, test$CH4na_anom, 48*2, normalize = T)
-conf_wm_TA <- lag_confidence(test$GPP_anom, test$CH4na_anom, 48*2, type = "TR", alpha = 0.05, runs = 20)
-
-Hours <- seq(0.5, 24*2, by = 0.5)
-
-plot(tr_wm_TA ~ Hours, type = "l", xlim = c(0,36), col = "black")
-points(conf_wm_TA ~ Hours, type = "l", col = "red")

### 2018-06-05 README.Rmd
README updates
add functional test and create error stops in significance functions

@@
 <!-- README.md is generated from README.Rmd. Please edit that file -->
+
+[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/salinity_study.svg?branch=master)](https://travis-ci.org/samdchamberlain/salinity_study)
 
@@
 
-# salinity
+# Salinity study
 
@@
 # install.packages("devtools")
-devtools::install_github("samdchamberlain/salinity")
+devtools::install_github("samdchamberlain/salinity_study")
 ```

### 2018-06-05 R/TR_functions.R

@@ -73,7 +73,7 @@ tr_timeseries <- function(x, y, data_list, lags, runs, bins = 10, alpha = 0.05, 
     } else if (type == "shuffled") {
       output_list[[name]] <- lag_confidence(x_var, y_var, lags, type = "TR", alpha, runs, bins, normalize)
     } else {
-      return("Warning: type not assigned correctly")
+      stop("Warning: type not assigned correctly")
     }
   }
   output_list

### 2018-06-05 R/signficance_tests.R

@@ -16,7 +16,7 @@ mi_confidence <- function(x, y, alpha = 0.05, runs = 100, bins = 10, normalize =
   if (alpha > 0 && alpha < 1) {
     limit <- quantile(mc_out, probs = (1 - alpha))[[1]]
   } else {
-    return("Error: sig. limit out of range (0 - 1).")
+    stop("Error: sig. limit out of range (0 - 1).")
   }
 
   # if (alpha == 0.01) {
@@ -42,7 +42,7 @@ tr_confidence <- function(x, y, xlag, ylag = 1, alpha = 0.05, runs = 25, bins = 
   if (alpha > 0 && alpha < 1) {
     limit <- quantile(mc_out, probs = (1 - alpha))[[1]]
   } else {
-    return("Error: sig. limit out of range (0 - 1).")
+    stop("Error: sig. limit out of range (0 - 1).")
   }
   # if (alpha == 0.01) {
   #   limit <- mean(mc_out) + 2.49*sd(mc_out)
@@ -70,7 +70,7 @@ conf_series <- function(x, y, data_list, alpha = 0.05, runs = 1000, bins = 10, t
     } else if (type == "TR") {
       MC_mean <- tr_confidence(x_var, y_var, alpha, runs, bins)
     } else {
-      return("Warning: not a valid test")
+      stop("Warning: not a valid test")
     }
 
     MC_series[[i]] <- MC_mean
@@ -93,7 +93,7 @@ lag_confidence <- function(x, y, lags, type = c("MI", "TR"), alpha,
       MC_lagseries[[i]] <- tr_confidence(x, y, xlag = i, ylag = 1, alpha, runs, bins, normalize)
     }
   } else {
-    return("Warning: not a valid test")
+    stop("Warning: not a valid test")
   }
   MC_lagseries
 }

### 2018-06-05 tests/testthat/test.R

@@ -1,0 +1,9 @@
+test_that("errors are thrown when they should be", {
+
+  x <- rnorm(100)
+  y <- rnorm(100, 2)
+
+  expect_error(mi_confidence(x, y, alpha = 1))
+  expect_error(tr_confidence(x, y, alpha = 0))
+
+})

### 2018-06-07 R/peat19_processing.R
remove use of 'wq' package no longer found on CRAN

@@ -5,12 +5,14 @@
 #' @import dplyr
 #' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
-#' @importFrom wq ec2pss
+
+# load ec2pss function
+source("R/transformations.R")
 
 # load eddy flux and met dataset
 load("data/peat19_all.Rdata")
 peat19_all$dday <- floor(peat19_all$decday)
-peat19_all$site <- "Baseline (mature)"
+peat19_all$site <- "Reference Wetland"
 peat19_all$sal <- ec2pss(peat19_all$conductivity, peat19_all$TW_8cm)
 
 #Simple average of daily fluxes for gapfilled values

### 2018-06-07 R/peat6_processing.R

@@ -5,13 +5,15 @@
 #' @import dplyr
 #' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
-#' @importFrom wq ec2pss
+
+# load ec2pss function
+source("R/transformations.R")
 
 # load eddy flux and met dataset
 load("data/peat6_all.Rdata")
 peat6_all$dday <- floor(peat6_all$decday)
 peat6_all$sal <- ec2pss(peat6_all$Cond, peat6_all$TW_TULE_10cm)
-peat6_all$site <- 'Salinity rise'
+peat6_all$site <- 'Salinization Wetland'
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%

### 2018-06-07 R/transformations.R

@@ -1,6 +1,8 @@
 #' Misc functions for data and list transformations:
 #' anom_filter - removes periodic signal from data
-#' 
+#' tidy_list - convert list format back into dataframe time series
+#' ec2pss (from wq package) - build issues with wq not on CRAN so moved directly to coded functions
+#'
 #'
 #' @importFrom dplyr lag
 #' @importFrom tidyr gather
@@ -12,56 +14,78 @@ anom_filter <- function(var, window = 5) {
 }
 
 tidy_list <- function(list) {
-  
+
   df <- as.data.frame(list)
   df$lag <- rownames(df) #rownames correspond to lag
   df <- gather(df, year, tr, -lag) #tidy with year by lag
   df$year <- str_replace(df$year, 'X', '') #clean up year column
   df <- map_df(df, as.numeric) #make all columns numeric
   df$hour <- df$lag/2
-  
+
   #create year index that also displays mean annual conductivity
-  
+
   return(df)
 }
 
+ec2pss <- function(ec, t, p = 0) {
+  R <- ec/42.914
+  c <- c(0.6766097, 0.0200564, 0.0001104259, -6.9698e-07, 1.0031e-09)
+  rt <- c[1] + c[2] * t + c[3] * t^2 + c[4] * t^3 + c[5] *
+    t^4
+  d <- c(0.03426, 0.0004464, 0.4215, -0.003107)
+  e <- c(2.07e-05, -6.37e-10, 3.989e-15)
+  Rp <- 1 + p * (e[1] + e[2] * p + e[3] * p^2)/(1 + d[1] *
+                                                  t + d[2] * t^2 + (d[3] + d[4] * t) * R)
+  Rt <- R/(Rp * rt)
+  a <- c(0.008, -0.1692, 25.3851, 14.0941, -7.0261, 2.7081)
+  b <- c(5e-04, -0.0056, -0.0066, -0.0375, 0.0636, -0.0144)
+  ft <- (t - 15)/(1 + 0.0162 * (t - 15))
+  S <- a[1] + a[2] * Rt^0.5 + a[3] * Rt + a[4] * Rt^1.5 + a[5] *
+    Rt^2 + a[6] * Rt^2.5 + ft * (b[1] + b[2] * Rt^0.5 + b[3] *
+                                   Rt + b[4] * Rt^1.5 + b[5] * Rt^2 + b[6] * Rt^2.5)
+  x <- 400 * Rt
+  y <- 100 * Rt
[…]

### 2018-06-27 R/peat6_processing.R
last updates v2, including data updates

@@ -79,7 +79,7 @@ monthly <- daily %>%
             days = sum(!is.na(mgCH4)),
             CH4_obs = sum(m_obs),
             total_obs = sum(t_obs)) %>%
-  filter(days > 27)  %>% # only complete months
+  #filter(days > 27)  %>% # only complete months (fix when new data arrives)
   mutate(frac_CH4obs = CH4_obs/total_obs)
 
 # convert to monthly sums

### 2018-08-23 R/peat6_processing.R
Updates for Ecosystems and fixed MI lagged confidence function

@@ -15,6 +15,9 @@ peat6_all$dday <- floor(peat6_all$decday)
 peat6_all$sal <- ec2pss(peat6_all$Cond, peat6_all$TW_TULE_10cm)
 peat6_all$site <- 'Salinization Wetland'
 
+#only include complete months (through May 2018)
+peat6_all <- subset(peat6_all, dday < 3074)
+
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%
   group_by(dday, site) %>%
@@ -79,7 +82,7 @@ monthly <- daily %>%
             days = sum(!is.na(mgCH4)),
             CH4_obs = sum(m_obs),
             total_obs = sum(t_obs)) %>%
-  #filter(days > 27)  %>% # only complete months (fix when new data arrives)
+  filter(days > 27)  %>% # only complete months
   mutate(frac_CH4obs = CH4_obs/total_obs)
 
 # convert to monthly sums

### 2018-08-23 R/signficance_tests.R

@@ -86,7 +86,7 @@ lag_confidence <- function(x, y, lags, type = c("MI", "TR"), alpha,
   if (type == "MI") {
     for (i in 1:(lags + 1)) {
       x_lag <- dplyr::lag(x, n = i-1) # include syncronhous interactions
-      MC_lagseries[[i]] <- mi_confidence(xlag, y, alpha, runs, bins, normalize)
+      MC_lagseries[[i]] <- mi_confidence(x_lag, y, alpha, runs, bins, normalize)
     }
   } else if (type == "TR") {
     for (i in 1:(lags)) {

### 2019-04-27 R/MI_functions.R
Revisions_round_1

@@ -55,7 +55,7 @@ mi_timeseries <- function(x, y, data_list, bins = 10, normalize = TRUE) {
 }
 
 #calculate correlation coefficients for comparison
-corr_timeseries <- function(x, y, data_list) {
+corr_timeseries <- function(x, y, data_list, method = 'kendall') {
 
   corr_series <- vector("double", nrow(data_list)) #vector to store correlation coefficients
 
@@ -65,7 +65,7 @@ corr_timeseries <- function(x, y, data_list) {
     x_var <- eval(substitute(x), current_df)
     y_var <- eval(substitute(y), current_df)
 
-    out <- cor.test(x_var, y_var, method = "kendall")
+    out <- cor.test(x_var, y_var, method = method)
     corr_series[[i]] <- out$estimate[[1]]
   }
   corr_series
